## Video Summary

I watched the talk titled *“Veri Bilimi ve Endüstri Mühendisliği Üzerine Sohbetler – Cem Vardar”*.  
In this talk, the speaker discusses the relationship between data science and industrial engineering.  
Industrial engineering focuses on optimization, efficiency, and analytical thinking, while data science
provides powerful tools for extracting insights from large datasets.

The speaker emphasizes that the integration of statistics, programming, and analytical reasoning
creates strong opportunities for industrial engineers in modern industries. With the increasing
availability of data, companies rely heavily on data-driven decision-making processes. Therefore,
engineers who understand data analysis tools such as R or Python can contribute significantly
to solving complex real-world problems.

Overall, the talk highlights how combining industrial engineering knowledge with data science
skills allows professionals to work in diverse sectors such as finance, logistics, technology,
and operations management.

---

## Open-ended Question

**Question:**  
Why is data science becoming increasingly important for industrial engineers?

**Answer:**  
Data science enables industrial engineers to analyze large datasets and generate insights that
improve operational and strategic decision-making. As industries become more data-driven,
engineers need data science skills to model systems, forecast trends, and optimize processes
based on real-world data.

---


## Multiple Choice Question

**Question:**  
Which of the following best describes how data science complements traditional industrial engineering methods?

A) It replaces optimization techniques with purely qualitative analysis  
B) It allows engineers to integrate statistical learning and large-scale data analysis into decision-making processes  
C) It eliminates the need for modeling complex systems  
D) It focuses only on software development rather than system improvement  

**Correct Answer:**  
B) It allows engineers to integrate statistical learning and large-scale data analysis into decision-making processes

---

## Data Analysis Tasks

```{r}
library(dslabs)

data(polls_us_election_2016)

data <- polls_us_election_2016
```

## Define Personal Variables

```{r}
my_first <- "Sevval"
my_birth_year <- 2003
```

## Define k

```{r}
k <- (nchar(my_first) + my_birth_year) %% 15 + 8
k
```

## Display Rows Based on k

```{r}
if(k %% 2 == 0){
  head(data, k)
} else {
  tail(data, k)
}
```

## Total Number of NA Values

```{r}
sum(is.na(data))
```

## NA Values Per Column (Top 8)

```{r}
na_counts <- colSums(is.na(data))
sort(na_counts, decreasing = TRUE)[1:8]
```

## Replace NA Values

```{r}
new_data <- data

for(col in names(new_data)){
  
  if(is.numeric(new_data[[col]])){
    
    new_data[[col]][is.na(new_data[[col]])] <- my_birth_year + k
    
  } else if(is.character(new_data[[col]]) | is.factor(new_data[[col]])){
    
    new_data[[col]][is.na(new_data[[col]])] <- paste0(my_first, "_", k)
    
  }
  
}
```

## Display k Rows of New Data

```{r}
if(k %% 2 == 0){
  head(new_data, k)
} else {
  tail(new_data, k)
}
```

## Remaining NA Values

```{r}
sum(is.na(new_data))
```

## Check if Any NA Remains

```{r}
anyNA(new_data)
```
